Mining Planet Search Data for Binary Stars: The $\psi^1$ Draconis system

### 2015-10-22 paper/ms.tex
Updated references.
All referee issues fixed.

\begin{abstract}
Several planet-search groups have acquired a great deal of data in the form of time-series spectra of several hundred nearby stars with time baselines of over a decade. While binary star detections are generally not the goal of these long-term monitoring efforts, the binary stars hiding in existing planet search data are precisely the type that are too close to the primary star to detect with imaging or interferometry techniques. We use a cross-correlation analysis to detect the spectral lines of a new low-mass companion to $\psi^1$ Draconis A, which has a known roughly equal-mass companion at $\sim 680$ AU. We measure the mass of $\psi^1$ Draconis C as $M_2 = 0.70 \pm 0.07 M_{\odot}$, with an orbital period of $\sim 20$ years. This technique could be used to characterize binary companions to many stars that show large-amplitude modulation or linear trends in radial velocity data.
\end{abstract}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{Resid_CCFs.pdf}
  \caption{Cross-correlation functions of a 4400 K model spectrum template with the data, after subtraction of the average CCF. Early dates are on bottom. The dark curve in the top middle is the signal of the companion star.}
  \label{fig:resids}
\end{figure}

@@

The companion radial velocities are measured relative to the primary star plus a small velocity shift ($\Delta v_2$) caused by a slight inaccuracies in the vacuum--to--air wavelength conversion in the model spectrum and spectrograph wavelength drift throughout the night. Finally, the CCF peak full-width at half maximum vastly over-estimates the velocity uncertainty and so we fit a scale factor ($f$) to apply to the companion velocity uncertainties. The uncertainties given in Table \ref{tab:rv_data} are already scaled by that factor. The full log-likelihood function ($\mathcal{L}$) is then given by:

@@

This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France, and of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
It was supported by a start-up grant to Adam Kraus from the University of Texas.

>>>>

\begin{abstract}
Several planet-search groups have acquired a great deal of data in the form of time-series spectra of several hundred nearby stars with time baselines of over a decade. While binary star detections are generally not the goal of these long-term monitoring efforts, the binary stars hiding in existing planet search data are precisely the type that are too close to the primary star to detect with imaging or interferometry techniques. We use a cross-correlation analysis to detect the spectral lines of a new low-mass companion to $\psi^1$ Draconis A, which has a known roughly equal-mass companion at ${\sim}680$ AU. We measure the mass of $\psi^1$ Draconis C as $M_2 = 0.70 \pm 0.07 M_{\odot}$, with an orbital period of ${\sim}20$ years. This technique could be used to characterize binary companions to many stars that show large-amplitude modulation or linear trends in radial velocity data.
\end{abstract}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{Resid_CCFs.pdf}
  \caption{Cross-correlation functions of a 4400 K model spectrum template with the data, after subtraction of the average CCF. The dark curve in the top middle is the signal of the companion star.}
  \label{fig:resids}
\end{figure}

@@

The companion radial velocities are measured relative to the primary star plus a small velocity shift ($\Delta v_2$) caused by slight inaccuracies in the vacuum--to--air wavelength conversion in the model spectrum and spectrograph wavelength drift throughout the night. Finally, the CCF peak full-width at half maximum vastly over-estimates the velocity uncertainty and so we fit a scale factor ($f$) to apply to the companion velocity uncertainties. The uncertainties given in Table \ref{tab:rv_data} are already scaled by that factor. The full log-likelihood function ($\mathcal{L}$) is then given by:

@@

This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France, and of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
It was supported by a start-up grant to Adam Kraus from the University of Texas. We would like to thank the referee for various suggestions that improved this paper.
